\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-02-11 doc/sw-publication-policy-cfhtls.tex
Updated plan for paper 1

\subsection{Journal Papers}
\label{sec:series}
A core team of collaborators will participate in writing journal papers, and many collaborators who have made a \textit{significant contribution} to \sw will be recognised on the author
lists of journal papers presenting \sw results.  However, not all collaboration members will participate in writing journal papers.  \textit{Significant contributions} include those who have contributed to:
\begin{itemize}
\item the site design, construction and operation
\item data preparation or analysis
\item writing and editing the papers. 
\end{itemize}

@@

\noindent The author categories are grouped according to collaboration membership (defined above). These groups of authors have either the status to ``opt-out'' or "on contribution" of \sw publications.  ``Opt-out'' means the listed people are authors by default and must explicitly state if they wish for their names to be removed from \sw publications. ``On contribution'' means the people listed are invited to comment on and contribute to publications. The Principal Investigators, Zooniverse development team and \sw Science team all have opt-out status and the \sw Affiliates have on contribution status.

>>>>

\subsection{Journal Papers}
\label{sec:series}

A core team of collaborators will participate in writing journal papers, and
many collaborators who have made a \textit{significant contribution} to \sw
will be recognised on the author lists of journal papers presenting \sw
results.  However, not all collaboration members will participate in writing
journal papers.  \textit{Significant contributions} include those who have
contributed to:
\begin{itemize}
\item the site design, construction and operation
\item data preparation or analysis
\item writing and editing the papers. 
\end{itemize}

@@

\noindent The author categories are grouped according to collaboration
membership (defined above). These groups of authors have either  ``opt-out''
or ``on contribution'' status regarding \sw publications.  ``Opt-out'' means
the listed people are authors by default and must explicitly state if they
wish for their names to be removed from \sw publications. ``On contribution''
indicates people who will be invited to comment on and contribute to
publications, ``opting in'' to those papers' author lists. The Principal
Investigators, Zooniverse development team and \sw Science team all have
opt-out status and the \sw Affiliates have on contribution status.

### 2014-02-11 doc/sw-system.tex
Updated plan for paper 1

\sw is a web-based service
 that enables the discovery of strong
gravitational lenses in wide-field imaging surveys by arbitrarily large
numbers of people. Carefully produced color composite images are
displayed to volunteers via a flexible interface, which records
their estimates of the positions of candidate lensed features. Simulated
lenses, and expert-classified non-lenses, are inserted into the stream
at random intervals; this training set is used to give the volunteers
feedback on their performance as well as estimate a dynamically-updated
probability for any given image containing a lens. High probability
systems are filtered into the Zooniverse \Talk discussion system; this
smaller sample is further classified and analysed by volunteers into a
final set. We analyze the classification of the training set itself, and
find that 1) $<$volunteers learn$>$... 2) $<$the filter works$>$...

@@

\begin{keywords}
  gravitational lensing   --
  methods: statistical    
\end{keywords}

@@

In this paper, we describe the \sw website, an online system that
enables crowd-sourced detection of gravitational lenses. 
Other papers in this series will present new gravitational lenses
discovered in our first imaging survey dataset, and investigate the
differences between lens detections made in \sw and those made with
automated techniques. Here, we try to answer the following questons:
\begin{itemize}

@@

\item How accurately can gravitational lenses be located on the sky
during the identification process?

\item How quickly can lenses be detected, and non-lenses be rejected?
How many volunteers are needed per target, and how quickly can they
mobilise?

@@

In \Sref{sec:design} we introduce the \sw system, describing and
explaining its various features. We then briefly

@@

Unfamiliar objects: need to learn what lenses look like, fast. Rare
objects: need to be able to reject rapidly, and get through sample.
Confusion with non-lenses: further filtering via scientific discussion
and further classification (voting).

@@

\subsection{Tutorial Material}
\label{sec:design:tutorial}

Learning what lenses do: Spotter's Guide and LensToy. Learning how
lenses work (science page, FAQ).

Inline tutorial. Merge into stream. Instant feedback, positive and
negative. Anecdotal support for this.

@@

\subsection{The Classification Interface}
\label{sec:design:classification}

Image presentation. Consistency in size and appearance.

Interface fast due to pre-loading of images, and minimizing interaction.

Spotting lenses: Markers to be placed. Two reasons: first, to give good
feedback. Second, to improve quality of discussion later.

@@

@@

@@

\subsection{Collaborative Filtering with ``Talk''}
\label{sec:design:classification}

Feeding in collections, following online analysis. 
Taking subjects to Talk individually, too.

Mental modeling. Further inspection on Dashboard. Voting.

Final sample generation.

@@

Training data and test data. Refer to Paper II for CFHTLS details.

Presentation of images. Arcsinh stretch, calibration. Approximately
optimized.

@@

\section{Identification Analysis}
\label{sec:IDanalysis}

@@

Where to describe probabilistic classifier stuff? Here or in an
appendix? Not sure.

@@

\section{Identification Results}
\label{sec:IDresults}

@@

\subsection{Learned Behavior}
\label{sec:results:learning}

@@

\subsection{Sample completeness and purity}
\label{sec:results:learning}

Vary the acceptance and rejection thresholds, look at completeness and
purity as a function of this. How much time can be saved by retiring
subjects into candidate list or rejection list?

@@

\item Ability to detect lenses

\item What we can say about the next steps

@@

Summarize, end.

>>>>

\sw is a web-based service that enables the discovery of strong gravitational
lenses in wide-field imaging surveys by large numbers of people. Carefully
produced color composite images are displayed to volunteers via a flexible
interface, which records their estimates of the positions of candidate lensed
features. Simulated lenses, and expert-classified non-lenses, are inserted
into the stream at random intervals; this training set is used to give the
volunteers feedback on their performance, and to estimate a
dynamically-updated probability for any given image to contain a lens. Low
probability systems are retired from the site daily, concentrating the sample
towards a set of candidates; these are then re-classified by the volunteers in
a second  refinement stage. Analyzing the classification of the training set,
we predict that the first stage should yield a sample with C\% completeness
and P\% purity, while leading to the rejection of R\% of the initial target
sample. Having divided the 150 square degree CFHTLS imaging survey into 430000
overlapping 70 by 70 arcminute tiles and displayed them on the site, we were
joined by 33000 volunteers who contributed X million image classifications
over the course of N months. The sample was reduced to 3500 stage 1
candidates; these were then refined to yield a sample of candidates rankable
by their stage 2 probability. We expect this sample to be X\% complete and Y\%
pure at a threshold of 95\% classification probability. We estimate the mean
information contributed per person to be X bits, over a session lasting, on
average, N classifications per volunteer -- although the distributions of
these quantities are highly skewed. We comment on the scalability of the \sw
system, and its potential to operate beyond its design as a supervised
classification system.

@@

\begin{keywords}
  gravitational lensing   --
  methods: statistical    --
  methods: citizen science
\end{keywords}

@@

In this paper, we describe the \sw website, an online system that enables
crowd-sourced detection of gravitational lenses.  In a companion paper we will
present the new gravitational lenses discovered in our first imaging survey
dataset, and begin to investigate the differences between lens detections made
in \sw and those made with automated techniques. Here though, we try to answer
the following questions:

@@

\item How quickly can lenses be detected, and non-lenses be rejected?
How many classifications, and so how many volunteers are needed per target?

\item What can we learn about the scalability of the crowd-sourcing approach?

@@

In \Sref{sec:design} we introduce the \sw system, describing and
explaining its various features. We then briefly...

@@

Unfamiliar objects: need to learn what lenses look like, fast. Rare
objects: need to be able to reject rapidly, and get through sample.
Confusion with non-lenses: further filtering after advanced training, and 
scientific discussion in Talk.

Intro to Classification Interface. Basic description of site.

@@

\subsection{Training}
\label{sec:design:training}

Learning what lenses do: Spotter's Guide. Learning how
lenses work (science page, FAQ).

More on what lenses do: inline tutorial and feedback. 
Merge into stream. Instant feedback, positive and
negative. Anecdotal support for this.

Training requires lenses to be more common than is realistic. How to manage
expectations, avoid high false positive rate? "Lenses are rare" messaging;
simulation frequency marker.

@@

\subsection{Stage 1: Initial Classification}
\label{sec:design:stage1}

Interface fast due to pre-loading of images, and minimizing interaction.
Trade-off between speed and accuracy. Decreasing training rate.

@@

Spotting lenses: Markers to be placed. Two reasons: first, to give good
feedback. Second, to focus attention.

@@

Retirement of low probability systems. Concentrates sample, provides more
``bacon'' (while slightly skewing "sim frequency"). Note that this feature
means that everyone contributes to detection of lenses: luck is made for the
few that happen to see the new lenses, by the masses that did the rejection.
Group effort.

Sims vs duds leads to inclusive search -- click on anything you think etc...

@@

\subsection{Stage 2: Refinement}
\label{sec:design:stage2}

Goal: assess candidates, reject false positives by comparing with training set
of non-obvious non-lenses. Produce a sample rankable by probability.

Reconfigured website: more detailed SG, more detailed feedback. Orange
background to make it obvious stage 2 is different. Slower image presentation.
Higher, constant training rate.

@@

Definitions: training subjects and test subjects. Sims and duds.

\subsection{The CFHT Legacy Survey}
\label{sec:data:CFHTLS}

Describe survey. Refs.

Why this one? Good IQ, deep, colorful, homogeneous. Precursor to Stage III and
IV imaging surveys, DES, KIDS, LSST etc. Already searched by robots: enables
comparison of techniques. Lenses not yet found by robots, detectable by
humans?

Blind search strategy.
Preparation of data: divide survey into overlapping tiles.

\subsection{Image Presentation}
\label{sec:data:display}

Presentation of images. Uniform scales, to build intuition and avoid rescales
due to bright objects. Arcsinh stretch, to bring out low SB features. 
Approximately optimized, how? Examples of images.

@@

\section{Classification Analysis}
\label{sec:IDanalysis}

@@

Describe SWAP here. (Move from appendix.)

@@

\section{Results}
\label{sec:results}

@@

\subsection{Crowd Properties}
\label{sec:results:crowd}

Enthusiasm: histogram of classifications, stage 1 vs stage 2. Information
contributed. Correlation with number of classifications.

PL and PD as measures of skill. not quite talent, due to possibility of
learning - but agents assume talent. Performance of crowd re PD and PL.
Correlations with N classifications.

@@

\subsection{Sample completeness and purity}
\label{sec:results:sample}

Rejection rate. Completeness and purity at P > retirement, P > 95\%, and 
as function of probability P. Compare stage 1 and stage 2.

Summarize performance at some fiducial threshold: eg P = 95\%.

@@

\item Crowd-sourced gravitational lens detection works, as shown on sims and duds:

\item Participation (crowd size, activity rate) enabled project completion

\item Both stages (1 and 2) achieved the required rejection rates

\item Integrated humanpower = X, cf hours taken by small team of experts

\item Nightly processing is inefficient: more classifications were made than
was necessary during peak participation. Need kafka...

\item Completeness and purity were estimated as C\% and P\%, from sim and dud
recovery/miss rates Which sims were missed? False negatives

\item The lens-finding crowd shows some interesting properties, with
consequences for future scalability

\item The information comes predominantly from volunteers with agents with P =
...

\item The agents show a high mean information per classification, which
increased/decreased with time; this does/doesn?t correlate with active crowd
size, showing how the crowd changed over time...

@@

Sum up, end.
